### 2024-01-02 documentation/thesis/thesis_document.tex
.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
\end{enumerate}

@@

\begin{itemize}
\item
  nummerieierung zuerst lokale sensoren dann weitere proxy sensoren
\item
  commando templating
\item
  einzelne sensor capabilites werden gemerged
\item
  ids werden aufsuimmiert
\item
  spätere sensor identifikation geschieht über die jeweilige sensor id,
  welche über diesen index abgefragt werden kann
\item
  tablle mit mergin algorithmus
\end{itemize}

@@

\begin{lstlisting}[language=Python]
from MRP import MRPReading, MRPMeasurementConfig
# [OPTIONAL] CONFIGURE READING USING MEASUREMENT CONFIG INSTANCE
config: MRPMeasurementConfig = MRPMeasurementConfig
config.sensor_distance_radius(40) # 40mm DISTANCE BETWEEN MAGNET AND SENSOR
config.magnet_type(N45_CUBIC_12x12x12) # CHECK MRPMagnetTypes.py FOR IMPLEMENTED TYPES
# CREATE READING
reading: MRPReading = MRPReading(config)
# ADD METADATA
reading.set_name("example reading")
## ADD FURTHER DETAILS
reading.set_additional_data("description", "abc")
reading.set_additional_data("test-number", 1)
# INSERT A DATAPOINT
measurement = MRPReadingEntry.MRPReadingEntry()
measurement.value = random.random()
reading.insert_reading_instance(measurement, False)
# USE MEASURED VALUES IN OTHER FRAMEWORKS / DATAFORMATS
## NUMPY
npmatrix: np.ndarray = reading.to_numpy_matrix()
## CSV
csv: []= reading.to_value_array()
## JSON
js: dict= reading.dump()
# EXPORT READING TO FILE
reading.dump_to_file("exported_reading.mag.json")

# IMPORT READING
imported_reading: MRPReading = MRPReading()
imported_reading.load_from_file("exported_reading.mag.json")
\end{lstlisting}

@@

\begin{lstlisting}[language=Python]
from MRP import MRPHalSerialPortInformation, MRPHal, MRPBaseSensor, MRPReadingSource
# SEARCH FOR CONNECTED SENSORS
system_ports: MRPHalSerialPortInformation = MRPHalSerialPortInformation.list_serial_ports()
sensor = MRPHal(system_ports[0])
# OR USE SPECIFIED SENSOR DEVICE
device_path: MRPHalSerialPortInformation = MRPHalSerialPortInformation("/dev/serial/by-name/UNFSensor1")
sensor = MRPHal(device_path)
# RAW SENSOR INTERACTION MODE
sensor.connect()
basesensor = MRPBaseSensor.MRPBaseSensor(sensor)
basesensor.query_readout()
print(basesensor.get_b()) # GET RAW MEASUREMENT
print(basesensor.get_b(1)) # GET RAW DATA FROM SENSOR WITH ID 1
# TO GENERATE A READING THE perform_measurement FUNCTION CAN BE USED
reading_source: MRPReadingSource = MRPReadingSourceHelper.createReadingSourceInstance(sensor)
result_readings: [MRPReading] = reading_source.perform_measurement(_readings=1, _hwavg=1)
\end{lstlisting}

>>>>

The following section defines some use cases that the future project
should be able to cover. They illustrate practical situations and help
to understand the functionality and added value of the implemented
project for the user. These were defined in the course of project
planning and provide an overview of how the user interacts with the
project and what functionalities can be expected. In the later
evaluation\ref{evaluation} process, the defined usecases are also used
as a reference to demonstrate the implemented capabilities of the
solution.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \textbf{Ready to use hardware sensor designs}
\item
  \textbf{Taking automatic measurements from sensors}
\item
  \textbf{Ready to use data analysis functions}
\item
  \textbf{Open storage formats for data export}
\item
  \textbf{Easy software configuration}
\item
  \textbf{User expandable data processing pipelines}
\end{enumerate}

@@

\begin{itemize}
\item
  nummerieierung zuerst lokale sensoren dann weitere proxy sensoren
\item
  commando templating
\item
  einzelne sensor capabilites werden gemerged
\item
  ids werden aufsuimmiert
\item
  spätere sensor identifikation geschieht über die jeweilige sensor id,
  welche über diesen index abgefragt werden kann
\item
  grafik mit mergin algorithmus
\end{itemize}

@@

The \passthrough{\lstinline!MRPReading!} module is the cornerstone of
the \gls{mrp} library. It is used to manage the measurement data and can
be imported and exported. The following
example\ref{lst:mrpexample_reading} shows how a measurement is created
and measurement points are added in the form of
\passthrough{\lstinline!MRPReadingEntry!} instances. An important point
is the management of the meta data, which further describes the
measurement. This is realised in the example using the
\passthrough{\lstinline!set\_additional\_data!} function.

\begin{lstlisting}[language=Python, caption={MRPReading example for setting up an basic measurement}, label=lst:mrpexample_reading]
from MRP import MRPReading, MRPMeasurementConfig
# [OPTIONAL] CONFIGURE READING USING MEASUREMENT CONFIG INSTANCE
config: MRPMeasurementConfig = MRPMeasurementConfig
config.sensor_distance_radius(40) # 40mm DISTANCE BETWEEN MAGNET AND SENSOR
config.magnet_type(N45_CUBIC_12x12x12) # CHECK MRPMagnetTypes.py FOR IMPLEMENTED TYPES
# CREATE READING
reading: MRPReading = MRPReading(config)
# ADD METADATA
reading.set_name("example reading")
## ADD FURTHER DETAILS
reading.set_additional_data("description", "abc")
reading.set_additional_data("test-number", 1)
# INSERT A DATAPOINT
measurement = MRPReadingEntry.MRPReadingEntry()
measurement.value = random.random()
reading.insert_reading_instance(measurement, False)
# USE MEASURED VALUES IN OTHER FRAMEWORKS / DATAFORMATS
## NUMPY
npmatrix: np.ndarray = reading.to_numpy_matrix()
## CSV
csv: []= reading.to_value_array()
## JSON
js: dict= reading.dump()
# EXPORT READING TO FILE
reading.dump_to_file("exported_reading.mag.json")
# IMPORT READING
imported_reading: MRPReading = MRPReading()
imported_reading.load_from_file("exported_reading.mag.json")
\end{lstlisting}

Finally, the measurement is exported for archiving and further
processing; various export formats are available. Using the
\passthrough{\lstinline!dump\_to\_file!} function, the measurement can
be converted into an open \gls{json} format. This file can then be
imported again at a later date using
\passthrough{\lstinline!load\_from\_file!}.

@@

After generating simple measurements with random values in the previous
example\ref{mrpreading}, the next step is to record real sensor data.
For this purpose, the MRPHal module was developed, which can interact
with all
\passthrough{\lstinline!Unified Sensor!}\ref{unified-sensor}-compatible
sensors. In the following example\ref{lst:mrpexample_hal}, an
\passthrough{\lstinline!1D: Single Sensor!}\ref{d-single-sensor} is
connected locally to the host \gls{pc}.

\begin{lstlisting}[language=Python, caption={MRPHal example to use an connected hardware sensor to store readings inside of an measurement}, label=lst:mrpexample_hal]
from MRP import MRPHalSerialPortInformation, MRPHal, MRPBaseSensor, MRPReadingSource
# SEARCH FOR CONNECTED SENSORS
## LISTS LOCAL CONNECTED OR NETWORK SENSORS
system_ports: MRPHalSerialPortInformation = MRPHalSerialPortInformation.list_sensors()
sensor = MRPHal(system_ports[0])
# OR USE SPECIFIED SENSOR DEVICE
device_path: MRPHalSerialPortInformation = MRPHalSerialPortInformation("UNFSensor1")
sensor = MRPHal(device_path)
# RAW SENSOR INTERACTION MODE
sensor.connect()
basesensor = MRPBaseSensor.MRPBaseSensor(sensor)
basesensor.query_readout()
print(basesensor.get_b()) # GET RAW MEASUREMENT
print(basesensor.get_b(1)) # GET RAW DATA FROM SENSOR WITH ID 1
# TO GENERATE A READING THE perform_measurement FUNCTION CAN BE USED
reading_source: MRPReadingSource = MRPReadingSourceHelper.createReadingSourceInstance(sensor)
result_readings: [MRPReading] = reading_source.perform_measurement(_readings=1, _hwavg=1)
\end{lstlisting}

In general, a sensor can be connected using its specific system path or
the sensor-\gls{id} via the MRPHalSerialPortInformation function.
Locally connected or network sensors can also be automatically
recognised using the \passthrough{\lstinline!list\_sensors!} function.
Once connected, these are then converted into a usable data source using
the MRPReadingSource module. This automatically recognises the type of
sensor and generated an \passthrough{\lstinline!MRPReading!} instance
with the measured values of the sensor.
